\documentclass[10pt,a4paper]{lettre}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
%\usepackage{lmodern}
% \usepackage[frenchb]{babel}

\usepackage{nopageno} % suppress page numbers
\usepackage{eurosym}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% LE FORMAT DE LA PAGE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\geometry
%   {%
%   paper=a4paper,%
%   margin=3cm,%
%   hoffset=0cm,%
   %headsep=0.5cm,%
%   }%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% EN-TÊTES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\pagestyle{empty}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% OPTIONS DES TABLEAUX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setlength{\tabcolsep}{1pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% OPTIONS DIVERSES : math, soulignement
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\parindent=18ex

%\usepackage[margin={0.6in,0.5in}]{geometry}
% \addtolength{\textheight}{4cm}
%\AtBeginDocument{\recomputelengths}
\addtolength{\textwidth}{2.5cm}
\addtolength{\oddsidemargin}{-2cm}


\begin{document}

\begin{letter}{QuantStack Paris\\27 Rue du Chemin Vert\\75011 PARIS\\France}
\name{Victor Cameo Ponz}
\address{Victor Cameo Ponz\\3 rue Tour Gayraud\\34 070 Montpellier}
\email{vicameo@free.fr}
\telephone{+33 (0)6.74.08.96.90}
\lieu{Montpellier}
\nofax

\conc{Application to Software Engineer - Python\&C++ / Package management}
\opening{Dear head of QuantStack, Sylvain Corlay,}

\parindent=6ex

Your advertisement for a Software Engineer in Python\&C++ and Package
management position has captured my interest. I believe I would be an excellent
fit for this job with regard to my experience as a software developer and in the
scientific computing field. Some key skills you will find relevant include:

\begin{itemize}
    \item proficient in developing Python code as well as manipulating C++ code from my
current position.
    \item used to working with git and commonly implemented workflows (issue/merge
request/CI).
    \item committed to automating most recurrent processes with Continuous Integration
tools.
    \item comfortable with scientific computing, from my current position and education.
    \item as an engineer from the support team, I'm used to detail user requests and
elaborate related solutions.
\end{itemize}


In my current position at CINES, I am involved in the installation and deployment
of hundreds of software on the tier 1 HPC cluster Occigen. I am working with
a variety of build tools and I am involved in the automation and industrialization
of the whole process.

I strongly believe in public sciences and free software through wide resources and
knowledge sharing. I have limited experience in the field of OpenSource and I
would be glad to improve it. Still, my understanding of this world is quite good
and I am used to submitting bug reports and feature requests using Github and Gitlab.
You can find an example of a contribution of mine to the code of EasyBuild, a
referenced HPC package manager written with python:
\href{https://github.com/easybuilders/easybuild-framework/pull/2457}
{$\hookrightarrow$ https://github.com/easybuilders/easybuild-framework/pull/2457}.

I'm looking for a dynamic team working with modern IT technology and
methodologies where my passionate and pragmatic personality could bloom.

I would welcome the opportunity to meet you for an in-depth interview to discuss
how we could work together.

\closing{Thank you for your time and consideration, sincerely,}
\end{letter}

\end{document}





